% ═══════════════════════════════════════════════════════════════════════
%  Section 7 — Roadmap
% ═══════════════════════════════════════════════════════════════════════

\section{Future Milestones}
\label{sec:roadmap}

With Milestone~2 establishing the security foundation, the remaining milestones layer on collaborative features and advanced security mechanisms.

\subsection{Milestone 3 — March 31, 2026 (2.5\%)}

Milestone~3 shifts focus from individual user features to multi-user interactions:

\begin{itemize}
    \item \textbf{Company pages and job postings} — Recruiters can create company profiles and publish job listings with titles, descriptions, required skills, location, and salary.
    \item \textbf{Job search} — Keyword search with filters for remote work, experience level, and skills.
    \item \textbf{Application tracking} — Candidates apply with their encrypted resumes. Application status flows through Applied $\rightarrow$ Reviewed $\rightarrow$ Interviewed $\rightarrow$ Offer/Rejected.
    \item \textbf{Encrypted messaging} — End-to-end encrypted 1:1 messaging between recruiters and candidates. The server stores only ciphertext.
\end{itemize}

\subsection{Milestone 4 — Final Evaluation — April 30, 2026}

The final milestone adds the most security-intensive features:

\begin{itemize}
    \item \textbf{PKI integration} — At least two functions backed by public key infrastructure (e.g., message signing, resume integrity verification via digital signatures).
    \item \textbf{OTP with virtual keyboard} — A visual on-screen keyboard for TOTP entry during high-risk actions (password reset, account deletion), defending against keyloggers.
    \item \textbf{Tamper-evident audit logs} — Hash chaining where each log entry includes the hash of the previous entry, making retroactive tampering detectable.
    \item \textbf{Attack demonstrations} — Live demonstrations of defense against SQL injection, XSS, CSRF, session fixation, and session hijacking.
\end{itemize}

\subsection{Bonus Targets}

\begin{itemize}
    \item \textbf{Blockchain audit logging (+6\%)} — Extending hash chaining into a lightweight blockchain structure for stronger tamper evidence.
    \item \textbf{Resume parsing (+2\%)} — NLP-based extraction of skills and experience from uploaded PDFs for automated candidate--job matching.
\end{itemize}
