% ═══════════════════════════════════════════════════════════════════════
%  Section 2 — Software Requirements Specification
% ═══════════════════════════════════════════════════════════════════════

\section{Software Requirements Specification}
\label{sec:requirements}

This section maps the course-specified requirements to our implementation plan. Each requirement is tagged with its target milestone and current status, making it easy to track progress across the semester.

\subsection{Authentication and Account Security}

The platform must provide robust identity management. Users register with email and password, where passwords must meet strength requirements and are stored using a memory-hard hashing algorithm (never in plaintext). Login must support TOTP-based two-factor authentication, with session management via secure, HttpOnly cookies. Account lockout must trigger after repeated failed attempts.

\begin{table}[H]
\centering
\small
\begin{tabular}{p{1cm} p{9cm} p{2.5cm}}
    \toprule
    \textbf{ID} & \textbf{Requirement} & \textbf{Status} \\
    \midrule
    AS-1 & Secure registration with password strength validation & M2 \checkmark \\
    AS-2 & Argon2id password hashing (64 MB, 3 iter) & M2 \checkmark \\
    AS-3 & TOTP two-factor authentication & M2 \checkmark \\
    AS-4 & JWT in HttpOnly, Secure, SameSite cookies & M2 \checkmark \\
    AS-5 & Device fingerprinting and session binding & M2 \checkmark \\
    AS-6 & Account lockout after 5 failed attempts & M2 \checkmark \\
    AS-7 & Refresh token rotation with reuse detection & M2 \checkmark \\
    \bottomrule
\end{tabular}
\end{table}

\subsection{User Profiles}

Users need to build a professional presence on the platform. This includes managing personal information, education history, work experience, and skills — all with input sanitization to prevent XSS attacks. Profile pictures undergo multi-layer validation (extension, MIME, magic bytes) before storage.

\begin{table}[H]
\centering
\small
\begin{tabular}{p{1cm} p{9cm} p{2.5cm}}
    \toprule
    \textbf{ID} & \textbf{Requirement} & \textbf{Status} \\
    \midrule
    UP-1 & Create/edit profiles (name, headline, bio, location) & M2 \checkmark \\
    UP-2 & Avatar upload with magic-byte validation & M2 \checkmark \\
    UP-3 & Education and experience management (CRUD) & M2 \checkmark \\
    UP-4 & Skills with autocomplete from curated list & M2 \checkmark \\
    UP-5 & Connection requests and privacy controls & M3 \\
    \bottomrule
\end{tabular}
\end{table}

\subsection{Secure Resume Storage}

Resumes are the most sensitive user asset on the platform. They must be encrypted at rest — meaning the server never stores plaintext resume content on disk. Downloads decrypt in memory and stream directly to the client. Access is restricted to the owner, authorized recruiters, and admins.

\begin{table}[H]
\centering
\small
\begin{tabular}{p{1cm} p{9cm} p{2.5cm}}
    \toprule
    \textbf{ID} & \textbf{Requirement} & \textbf{Status} \\
    \midrule
    SR-1 & PDF upload with multi-layer validation & M2 \checkmark \\
    SR-2 & Fernet encryption at rest (AES-128-CBC + HMAC) & M2 \checkmark \\
    SR-3 & Owner/recruiter/admin-only access control & M2 \checkmark \\
    SR-4 & UUID filenames to prevent path traversal & M2 \checkmark \\
    \bottomrule
\end{tabular}
\end{table}

\subsection{Admin Dashboard}

Platform admins require visibility into user activity and the ability to moderate accounts. The dashboard must support user management (listing, role changes, suspension, deletion) and access to audit logs that record every security-relevant event.

\begin{table}[H]
\centering
\small
\begin{tabular}{p{1cm} p{9cm} p{2.5cm}}
    \toprule
    \textbf{ID} & \textbf{Requirement} & \textbf{Status} \\
    \midrule
    AD-1 & Admin dashboard with user list and search & M2 \checkmark \\
    AD-2 & RBAC: User, Recruiter, Admin roles & M2 \checkmark \\
    AD-3 & Suspend/unsuspend accounts & M2 \checkmark \\
    AD-4 & Delete accounts with cascade cleanup & M2 \checkmark \\
    AD-5 & Audit log viewer with filters & M2 \checkmark \\
    \bottomrule
\end{tabular}
\end{table}

\subsection{Upcoming Requirements (Milestones 3--4)}

The following requirements are planned for future milestones:

\begin{itemize}
    \item \textbf{M3:} Company pages, job postings, search with filters, application tracking, encrypted messaging
    \item \textbf{M4:} PKI integration (message signing, resume integrity), OTP virtual keyboard for high-risk actions, tamper-evident audit logs (hash chaining), defense demonstrations against SQL injection, XSS, CSRF, and session attacks
\end{itemize}

\subsection{User Roles}

The platform defines three roles with escalating privileges. Access control is enforced at the API layer via FastAPI's dependency injection — every protected endpoint passes through a role checker before any business logic executes.

\begin{enumerate}
    \item \textbf{Regular User} — manages own profile, uploads resumes, applies to jobs
    \item \textbf{Recruiter / Company Admin} — additionally creates company pages, posts jobs, views applicants
    \item \textbf{Platform Admin} — full access to user management, moderation, and audit logs
\end{enumerate}
